### 2017-10-14 paper/sexSelectionSpacingAppendix-ver1.tex
Create parity progression graphs for spell 1 for Appendix

>>>>

\begin{figure}[htpb]
\centering
\caption*{No Education}
\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_low_urban_pps}} 
\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_low_rural_pps}} \\
\caption*{1-7 Years of Education}
\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_med_urban_pps}} 
\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_med_rural_pps}} \\
\caption*{8 or more Years of Education}
\subfloat[Urban]{\includegraphics[width=0.49\textwidth]{spell1_high_urban_pps}} 
\subfloat[Rural]{\includegraphics[width=0.49\textwidth]{spell1_high_rural_pps}} 
\caption{[Parity progression conditional survival]}
\label{fig:results_spell1_pps}
\end{figure}
